---
title: "clean clean clean <3"
author: "Naomi Liftman"
date: "2/23/2022"
output: pdf_document
---
# Load Files
```{r}
#load all necessary packages
library(tidyverse)
library(psych)
library(mosaic)
library(nlme)
```

# Import Premeasures and Clean
```{r}
#import the data
pre <- read_csv("TeleCom_Dyad_premeasures.csv")

#clean the data so it is numeric
pre <- pre %>%
  mutate(asi_1 = as.numeric(gsub("[a-zA-Z]", "", asi_1)),
         asi_2 = as.numeric(gsub("[a-zA-Z]", "", asi_2)),
         asi_3 = as.numeric(gsub("[a-zA-Z]", "", asi_3)),
         asi_4 = as.numeric(gsub("[a-zA-Z]", "", asi_4)),
         asi_5 = as.numeric(gsub("[a-zA-Z]", "", asi_5)),
         asi_6 = as.numeric(gsub("[a-zA-Z]", "", asi_6)),
         asi_7 = as.numeric(gsub("[a-zA-Z]", "", asi_7)),
         asi_8 = as.numeric(gsub("[a-zA-Z]", "", asi_8)),
         asi_9 = as.numeric(gsub("[a-zA-Z]", "", asi_9)),
         asi_10 = as.numeric(gsub("[a-zA-Z]", "", asi_10)),
         asi_11 = as.numeric(gsub("[a-zA-Z]", "", asi_11)),
         asi_12 = as.numeric(gsub("[a-zA-Z]", "", asi_12)),
         asi_13 = as.numeric(gsub("[a-zA-Z]", "", asi_13)),
         asi_14 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_15 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_16 = as.numeric(gsub("[a-zA-Z]", "", asi_16)),
         asi_17 = as.numeric(gsub("[a-zA-Z]", "", asi_17)),
         asi_18 = as.numeric(gsub("[a-zA-Z]", "", asi_18)),
         asi_19 = as.numeric(gsub("[a-zA-Z]", "", asi_19)),
         asi_20 = as.numeric(gsub("[a-zA-Z]", "", asi_20)),
         asi_21 = as.numeric(gsub("[a-zA-Z]", "", asi_21)),
         asi_22 = as.numeric(gsub("[a-zA-Z]", "", asi_22)))

#reversing all the variables that need it 
pre <- pre %>% 
  mutate(asi_3.r = (1+6) - asi_3,
         asi_6.r = (1+6) - asi_6,
         asi_7.r = (1+6) - asi_7,
         asi_13.r = (1+6) - asi_13,
         asi_18.r = (1+6) - asi_18,
         asi_21.r = (1+6) - asi_21)
```

# Look at benevolent
```{r}
#pull out for benevolent sexism
benevbaby <- pre %>% 
  select(dyadID, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, asi_17, asi_19, asi_20, asi_22)

#benevolent correlation matrix
corr.test(select(benevbaby, asi_1:asi_22))$r
```

# Look at hostile
```{r}
#pull out for hostile sexism
hostilebaby <- pre %>% 
  select(dyadID, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, asi_15, asi_16, asi_18.r, asi_21.r)

#hostile correlation matrix
corr.test(select(hostilebaby, asi_2:asi_21.r))$r
#question 18 is still giving us problems :(, where in the actual qualtrics survey
#the question should be reversed but maybe ppl just didnt understand the question
#should we get rid of the question? idk
```

# Calculate reliability
```{r}
#reliability for the benevolent
alpha(select(benevbaby, asi_1:asi_22))
#raw alpha is 0.8001697

#reliability for the hostile
alpha(select(hostilebaby, asi_2:asi_21.r))
#raw alpha is 0.8549932
```

# Actually Creating Scale Scores
```{r}
#the alpha for both of our variables is above .7, so we are swag
#now we are going to merge the new datasets back together
pre_fixed <- benevbaby %>% 
  inner_join(hostilebaby, by = "dyadID")

#benevolent own variable
pre_fixed$benevolaet <- rowMeans(select(pre_fixed, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, asi_17, asi_19, asi_20, asi_22))

#hostile own variable not included 18, because it is fricked
pre_fixed$hostile <- rowMeans(select(pre_fixed, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, asi_15, asi_16, asi_21.r))
```

# Daily
```{r}
#import data
daily <- read_csv("TeleCom_Dyad_dailydiary.csv")

#cleaning data to only include our sample size and the variables we are measuring
daily <- daily %>%
  select(dyadID, RecordedDate, gender, beds:calls, qmi4) 

#loading the premeasures data, but only including the dyad ID and the sexualor
sexor <- read_csv("TeleCom_Dyad_premeasures.csv") %>%
  select(dyadID, sexualor)
  
#creating a data with both premeasures and daily
#remove all that are not heterosexual
total <- daily %>%
  left_join(sexor, by = "dyadID") %>%
  filter(sexualor == "Heterosexual")

# Making chore data numeric
total <- total %>%
  select(-cars, -events) %>%
  mutate(beds = if_else(beds == "Yes", 1, 0),
         vacuum = if_else(vaccum == "Yes", 1, 0),
         food = if_else(food == "Yes", 1, 0),
         dishes = if_else(dishes == "Yes", 1, 0),
         garbage = if_else(garbage == "Yes", 1, 0),
         yardwork = if_else(yardwork == "Yes", 1, 0),
         pets = if_else(pets == "Yes", 1, 0),
         laundry = if_else(laundry == "Yes", 1, 0),
         errands = if_else(errands == "Yes", 1, 0),
         finances = if_else(finances == "Yes", 1, 0),
         calls = if_else(calls == "Yes", 1, 0)) %>%
  select(-vaccum, sexualor) %>%
  distinct()

#replacing all the qmis with character strings of numbers
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Mostly true about me', 1)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Somewhat true about me', 2)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'A little true about me', 3)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Not true about me', 4)

#makeing the character strings of numbers actually numeric
allnumeric <- total %>% 
  mutate(qmi4 = as.numeric(qmi4))
``` 

```{r}
#remove all the nas? 
allnumeric[, 4:13][is.na(allnumeric[, 4:13])] <- 0

#creating the individual chore number by summing
#get rid of other parts of the other parts of the recorded date so its only day
allnumeric <- allnumeric %>%
  rowwise() %>%
  mutate(ind_chores = sum(beds, food, dishes, garbage, yardwork, pets, laundry, errands, finances, calls, vacuum),
         RecordedDate = substr(RecordedDate, 1, 7))

#creating a new dataset with only the couple chores
couple_chores <- allnumeric %>%
  group_by(dyadID, RecordedDate) %>%
  summarize(cup_chores = sum(ind_chores))

#a combination of both the chores the partner and the actor did
total_chores <- couple_chores %>%
  right_join(couple_chores, by = c("dyadID", "RecordedDate"))

#finding the daily chores performed per day
total_chores <- total_chores %>%
  group_by(dyadID, RecordedDate, gender) %>%
  summarize(daily_per = ind_chores / cup_chores)

#finding the average amount of chores done over the 14 day period
final_chores <- happy_chores %>%
  group_by(dyadID, gender) %>%
  summarize(avg_per = sum(daily_per)/14)

#CRY CRY NAOMI TIME and messing with qmi



```



# Task 1
Scale for each variable: 

We are using the Ambivalent Sexism Inventory to calculate scores for benevolent (BS) and hostile (HS) sexism. This scale has 22 questions with 11 pertaining to each type of sexism. We did remove one question which was supposed to be reverse scored; however, the participants clearly did not understand the question, and their responses were not what we would expect. For these reason we are omitting the question, "There are actually very few women who get a kick out of teasing men by seeming sexually available and then refusing male advances". (USE THE ASI)

To calculate the division of household labor we are asking each person what chores they completed that day out of a 11 total possible chores. We asked them to indicate "Today, did you spend any time on the following household chores? If the item is not applicable (for example, you don't have any pets), please leave this item blank." and then gave them a list of chores, for which they had to answer no or yes below. We have only included chores that are completely routinely (around every day), which include items such as "made beds or changed bed linens" and "washed dishes today".

Finally for our response variable of how much of a team the participant feels they are with their partner we asked them "Please indicate the degree to which you identify with the following statements about your romantic relationship today" and the question "Today, my partner and I are really a team". This was calculated on a four point scale with one being the answer 'mostly true about me' and four being the response "Not true about me". 




# Task 2
```{r}
demographics <- read_csv("TeleCom_Dyad_premeasures.csv") %>%
  filter(sexualor == "Heterosexual") %>%
  select(gender, race, parttime, people_4_TEXT, people_5_TEXT)

hmmm <- read_csv("TeleCom_Dyad_premeasures.csv") %>%
  select(sexualor, gender)

hmmm %>%
  group_by(sexualor, gender) %>%
  summarize(n = n())

```

While the original data set includes 364 participants of all identities, it predominantly consists of heterosexual individuals (n = 353). In order to look at division of labor along gender lines, it is necessary to restrict the data set to male-female couples. Due to the small number of male-female couples that included an individual who was not heterosexual, we decided to restrict our sample futher to only include heterosexual couples. This was done in order to prevent any confounds that sexual orientation may have caused. Additionally 

- relationships

- Describe any exclusion criteria used
- Report sample size (number of individuals as well as number of dyads)
- Report basic demographics for the sample. That is, percentages of gender, percentages of racial groups, participant age, major, income, age of children, adoption type, etc. This depends, of course, on what you have in your data
- If working with distinguishable dyads, report the correlations among important study variables using the dyad dataset. I recommend doing this in a table, NOT by reporting each correlation in the text
- If working with distinguishable dyads, you can run some paired-samples t-tests using the dyad dataset to test for basic differences
