---
title: "clean clean clean <3"
author: "Naomi Liftman"
date: "2/23/2022"
output: pdf_document
---
# Load Files
```{r}
#load all necessary packages
library(tidyverse)
library(psych)
```

# Import Premeasures and Clean
```{r}
#import the data
pre <- read_csv("TeleCom_Dyad_premeasures.csv")

#clean the data so it is numeric
pre <- pre %>%
  mutate(asi_1 = as.numeric(gsub("[a-zA-Z]", "", asi_1)),
         asi_2 = as.numeric(gsub("[a-zA-Z]", "", asi_2)),
         asi_3 = as.numeric(gsub("[a-zA-Z]", "", asi_3)),
         asi_4 = as.numeric(gsub("[a-zA-Z]", "", asi_4)),
         asi_5 = as.numeric(gsub("[a-zA-Z]", "", asi_5)),
         asi_6 = as.numeric(gsub("[a-zA-Z]", "", asi_6)),
         asi_7 = as.numeric(gsub("[a-zA-Z]", "", asi_7)),
         asi_8 = as.numeric(gsub("[a-zA-Z]", "", asi_8)),
         asi_9 = as.numeric(gsub("[a-zA-Z]", "", asi_9)),
         asi_10 = as.numeric(gsub("[a-zA-Z]", "", asi_10)),
         asi_11 = as.numeric(gsub("[a-zA-Z]", "", asi_11)),
         asi_12 = as.numeric(gsub("[a-zA-Z]", "", asi_12)),
         asi_13 = as.numeric(gsub("[a-zA-Z]", "", asi_13)),
         asi_14 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_15 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_16 = as.numeric(gsub("[a-zA-Z]", "", asi_16)),
         asi_17 = as.numeric(gsub("[a-zA-Z]", "", asi_17)),
         asi_18 = as.numeric(gsub("[a-zA-Z]", "", asi_18)),
         asi_19 = as.numeric(gsub("[a-zA-Z]", "", asi_19)),
         asi_20 = as.numeric(gsub("[a-zA-Z]", "", asi_20)),
         asi_21 = as.numeric(gsub("[a-zA-Z]", "", asi_21)),
         asi_22 = as.numeric(gsub("[a-zA-Z]", "", asi_22)))

#reversing all the variables that need it 
pre <- pre %>% 
  mutate(asi_3.r = (1+6) - asi_3,
         asi_6.r = (1+6) - asi_6,
         asi_7.r = (1+6) - asi_7,
         asi_13.r = (1+6) - asi_13,
         asi_18.r = (1+6) - asi_18,
         asi_21.r = (1+6) - asi_21)
```

# Look at benevolent
```{r}
#pull out for benevolent sexism
benevbaby <- pre %>% 
  select(dyadID, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, asi_17, asi_19, asi_20, asi_22)

#benevolent correlation matrix
corr.test(select(benevbaby, asi_1:asi_22))$r
```

# Look at hostile
```{r}
#pull out for hostile sexism
hostilebaby <- pre %>% 
  select(dyadID, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, asi_15, asi_16, asi_18.r, asi_21.r)

#hostile correlation matrix
corr.test(select(hostilebaby, asi_2:asi_21.r))$r
#question 18 is still giving us problems :(, where in the actual qualtrics survey
#the question should be reversed but maybe ppl just didnt understand the question
#should we get rid of the question? idk
```

# Calculate reliability
```{r}
#reliability for the benevolent
alpha(select(benevbaby, asi_1:asi_22))
#raw alpha is 0.8001697

#reliability for the hostile
alpha(select(hostilebaby, asi_2:asi_21.r))
#raw alpha is 0.8549932
```

# Actually Creating Scale Scores
```{r}
#the alpha for both of our variables is above .7, so we are swag
#now we are going to merge the new datasets back together
pre_fixed <- benevbaby %>% 
  inner_join(hostilebaby, by = "dyadID")

#benevolent own variable
pre_fixed$benevolaet <- rowMeans(select(pre_fixed, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, asi_17, asi_19, asi_20, asi_22))

#hostile own variable not included 18, because it is fricked
pre_fixed$hostile <- rowMeans(select(pre_fixed, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, asi_15, asi_16, asi_21.r))
```

# Daily
```{r}
daily <- read_csv("TeleCom_Dyad_dailydiary.csv")

#cleaning data to only include our sample size and the variables we are measuring
daily <- daily %>%
  select(dyadID, RecordedDate, gender, beds:calls, qmi4) 

sexor <- read_csv("TeleCom_Dyad_premeasures.csv") %>%
  select(dyadID, sexualor)
  
chores <- daily %>%
  left_join(sexor, by = "dyadID") %>%
  filter(sexualor == "Heterosexual")

# Making chore data numeric
chores <- chores %>%
  select(-cars, -events) %>%
  mutate(beds = if_else(beds == "Yes", 1, 0),
         vacuum = if_else(vaccum == "Yes", 1, 0),
         food = if_else(food == "Yes", 1, 0),
         dishes = if_else(dishes == "Yes", 1, 0),
         garbage = if_else(garbage == "Yes", 1, 0),
         yardwork = if_else(yardwork == "Yes", 1, 0),
         pets = if_else(pets == "Yes", 1, 0),
         laundry = if_else(laundry == "Yes", 1, 0),
         errands = if_else(errands == "Yes", 1, 0),
         finances = if_else(finances == "Yes", 1, 0),
         calls = if_else(calls == "Yes", 1, 0)) %>%
  select(-vaccum, sexualor) %>%
  distinct()
``` 

```{r}
chores[, 4:13][is.na(chores[, 4:13])] <- 0

chores <- chores %>%
  rowwise() %>%
  mutate(ind_chores = sum(beds, food, dishes, garbage, yardwork, pets, laundry, errands, finances, calls, vacuum))

chores <- chores %>% 
  mutate(RecordedDate = substr(RecordedDate, 1, 7))

total_chores <- chores %>%
  group_by(dyadID, RecordedDate) %>%
  summarize(cup_chores = sum(ind_chores))

happy_happy_happy <- chores %>%
  right_join(total_chores, by = c("dyadID", "RecordedDate"))

happy_chores <- happy_happy_happy %>%
  group_by(dyadID, RecordedDate, gender) %>%
  summarize(daily_per = ind_chores / cup_chores)

final_chores <- final_chores %>%
  group_by(dyadID, gender) %>%
  summarize(avg_per = sum(daily_per)/14)

#CRY CRY NAOMI TIME
```

# Task 1

# Task 2
```{r}
demographics <- read_csv("TeleCom_Dyad_premeasures.csv") %>%
  filter(sexualor == "Heterosexual") %>%
  select(gender, race, parttime, people_4_TEXT, people_5_TEXT)
```

Since our analysis looks at division of labor based on gender, we restricted our sample to only include heterosexual couples. Since all of the couples are living together, it did not seem necessary to distinguish between committed relationships and marriage.

- Describe any exclusion criteria used
- Report sample size (number of individuals as well as number of dyads)
- Report basic demographics for the sample. That is, percentages of gender, percentages of racial groups, participant age, major, income, age of children, adoption type, etc. This depends, of course, on what you have in your data
- If working with distinguishable dyads, report the correlations among important study variables using the dyad dataset. I recommend doing this in a table, NOT by reporting each correlation in the text
- If working with distinguishable dyads, you can run some paired-samples t-tests using the dyad dataset to test for basic differences
