---
title: "JESUS (actually moses, we are jews)"
author: "Naomi Liftman"
date: "4/4/2022"
output: pdf_document
---
```{r include = FALSE, message = FALSE, warning = FALSE}
#loading all the files
library(tidyverse)
library(lubridate)
library(psych)
library(mosaic)
library(nlme)
library(kableExtra)
```

```{r}
#PREMEASURES
# Loading the data 
pre <- read_csv("TeleCom_Dyad_premeasures.csv")

pre <- pre %>% 
  select(ResponseId, dyadID, Q138, cohabitation, wfh, gender, sexualor, race, 
         religion, conservatism, people_4_TEXT, people_5_TEXT, indinc, 
         asi_1:asi_22)

# Making ASI numeric
pre <- pre %>%
  mutate(asi_1 = as.numeric(gsub("[a-zA-Z]", "", asi_1)),
         asi_2 = as.numeric(gsub("[a-zA-Z]", "", asi_2)),
         asi_3 = as.numeric(gsub("[a-zA-Z]", "", asi_3)),
         asi_4 = as.numeric(gsub("[a-zA-Z]", "", asi_4)),
         asi_5 = as.numeric(gsub("[a-zA-Z]", "", asi_5)),
         asi_6 = as.numeric(gsub("[a-zA-Z]", "", asi_6)),
         asi_7 = as.numeric(gsub("[a-zA-Z]", "", asi_7)),
         asi_8 = as.numeric(gsub("[a-zA-Z]", "", asi_8)),
         asi_9 = as.numeric(gsub("[a-zA-Z]", "", asi_9)),
         asi_10 = as.numeric(gsub("[a-zA-Z]", "", asi_10)),
         asi_11 = as.numeric(gsub("[a-zA-Z]", "", asi_11)),
         asi_12 = as.numeric(gsub("[a-zA-Z]", "", asi_12)),
         asi_13 = as.numeric(gsub("[a-zA-Z]", "", asi_13)),
         asi_14 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_15 = as.numeric(gsub("[a-zA-Z]", "", asi_15)),
         asi_16 = as.numeric(gsub("[a-zA-Z]", "", asi_16)),
         asi_17 = as.numeric(gsub("[a-zA-Z]", "", asi_17)),
         asi_18 = as.numeric(gsub("[a-zA-Z]", "", asi_18)),
         asi_19 = as.numeric(gsub("[a-zA-Z]", "", asi_19)),
         asi_20 = as.numeric(gsub("[a-zA-Z]", "", asi_20)),
         asi_21 = as.numeric(gsub("[a-zA-Z]", "", asi_21)),
         asi_22 = as.numeric(gsub("[a-zA-Z]", "", asi_22)))

# Reverse-coding relevant questions 
pre <- pre %>% 
  mutate(asi_3.r = (1+6) - asi_3,
         asi_6.r = (1+6) - asi_6,
         asi_7.r = (1+6) - asi_7,
         asi_13.r = (1+6) - asi_13,
         asi_18.r = (1+6) - asi_18,
         asi_21.r = (1+6) - asi_21)

# Benevolent correlation matrix
corr.test(select(pre, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, 
                 asi_17, asi_19, asi_20, asi_22))$r

# Hostile correlation matrix
corr.test(select(pre, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, 
                 asi_15, asi_16, asi_21.r))$r
#we did not include question 18

# ASI reliability
# Reliability for the benevolent
alpha(select(pre, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, asi_13.r, 
             asi_17, asi_19, asi_20, asi_22))
#raw alpha is 0.8001697

# Reliability for the hostile
alpha(select(pre, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, asi_14, 
             asi_15, asi_16, asi_21.r))
#raw alpha is 0.8743657 without question 18

# Benevolent own variable
pre$bs <- rowMeans(select(pre, asi_1, asi_3.r, asi_6.r, asi_8, asi_9, asi_12, 
                          asi_13.r, asi_17, asi_19, asi_20, asi_22))

# Hostile own variable, without question 18
pre$hs <- rowMeans(select(pre, asi_2, asi_4, asi_5, asi_7.r, asi_10, asi_11, 
                          asi_14, asi_15, asi_16, asi_21.r))
```

```{r}
#DAILY
# Loading the data
daily <- read_csv("TeleCom_Dyad_dailydiary.csv")

daily <- daily %>%
  mutate(RecordedDate = mdy_hm(RecordedDate)) %>%
  arrange(dyadID, partID, day, RecordedDate) %>%
  mutate(ResponseID = seq_along(RecordedDate)) %>%
  group_by(partID, day) %>%
  mutate(RecordedDate_lag = lag(RecordedDate), #so we can test if record for second tuesday are plausibly next week
         dist = difftime(RecordedDate, RecordedDate_lag, units = "days"), #recoding as day between
         first_sec = seq_along(RecordedDate), #first tuesday or second tuesday?
         prob = ifelse(first_sec >= 2 & dist < 4, 1, 0)) %>% #second+ tuesday is problematic if it's NOT plausibly next week
  group_by(dyadID, partID) %>%
  arrange(dyadID, partID, RecordedDate) %>%
  mutate(rec_num = seq_along(RecordedDate),
         weekish = ifelse(rec_num > 7, 2, 1), #coding for days beyond 7, most are "week 2"
         day_of_study = ifelse(weekish == 2 | (weekish==1 & first_sec>1), #for people who missed days in week 1
                        (case_when(day == "Monday" ~ 8,
                        day == "Tuesday" ~ 9,
                        day == "Wednesday" ~ 10,
                        day == "Thursday" ~ 11,
                        day == "Friday" ~ 12,
                        day == "Saturday" ~ 13,
                        day == "Sunday" ~ 14)), 
                      case_when(day == "Monday" ~ 1,
                        day == "Tuesday" ~ 2,
                        day == "Wednesday" ~ 3,
                        day == "Thursday" ~ 4,
                        day == "Friday" ~ 5,
                        day == "Saturday" ~ 6,
                        day == "Sunday" ~ 7)),
         week = ifelse(day_of_study > 7, 2, 1)) %>%
  group_by(partID) %>%
  mutate(problems = sum(prob)) %>%
  arrange(desc(problems), dyadID, partID, RecordedDate) %>%
  select(ResponseID, partID_given:day, day_of_study, RecordedDate_lag, dist, 
         first_sec, prob, rec_num,  
          weekish, week, problems, gender:comments)

#remove anyone with 
#(problems > 1) | (problems == 1 & !is.na(partID_given)) 
daily <- daily %>% 
  filter((problems <= 1) | (problems != 1) & (!is.na(partID_given)))

#other problematic cases or IDs to filter out completely: 
#146, 1266, 1278, 1282, 1302, partID == R_1fiPEJydpvuaEEs, R_1jV9NyWEbelB76s,R_1PTxhk4207mTHAb, R_27kuznipTrWICLB, 2800
daily <- daily %>% 
  filter(ResponseID != 146, ResponseID != 1266, ResponseID != 1278,  
         ResponseID != 1282, ResponseID != 1302, ResponseID != 2800) %>% 
  filter(partID != 'R_1fiPEJydpvuaEEs', partID != 'R_1jV9NyWEbelB76s', 
         partID != 'R_1PTxhk4207mTHAb', partID != 'R_27kuznipTrWICLB')

#other problematic cases to fix due to participant error:
daily <- daily %>% 
  mutate(day = ifelse(ResponseID == 494, "Friday", day),
         day = ifelse(ResponseID == 771, "Wednesday", day),
         day = ifelse(ResponseID == 873, "Monday", day),
         day = ifelse(ResponseID == 887, "Monday", day),
         day = ifelse(ResponseID == 1077, "Wednesday", day),
         day = ifelse(ResponseID == 1111, "Saturday", day),
         day = ifelse(ResponseID == 1202, "Wednesday", day),
         day = ifelse(ResponseID == 1219, "Tuesday", day),
         day = ifelse(ResponseID == 1233, "Tuesday", day),
         day = ifelse(ResponseID == 1247, "Tuesday", day),
         day = ifelse(ResponseID == 1365, "Saturday", day),
         day = ifelse(ResponseID == 1771, "Friday", day),
         day = ifelse(ResponseID == 1785, "Friday", day),
         day = ifelse(ResponseID == 2328, "Wednesday", day),
         day = ifelse(ResponseID == 2345, "Saturday", day),
         day = ifelse(ResponseID == 2393, "Wednesday", day),
         day = ifelse(ResponseID == 2516, "Thursday", day),
         day = ifelse(ResponseID == 2680, "Monday", day),
         day = ifelse(ResponseID == 2694, "Monday", day),
         day = ifelse(ResponseID == 2821, "Saturday", day),
         day = ifelse(ResponseID == 2825, "Sunday", day),
         day = ifelse(ResponseID == 2859, "Wednesday", day),
         day = ifelse(ResponseID == 2881, "Sunday", day),
         day = ifelse(ResponseID == 2940, "Thursday", day),
         day = ifelse(ResponseID == 3005, "Monday", day),
         day = ifelse(ResponseID == 3025, "Thursday", day),
         day = ifelse(ResponseID == 3178, "Monday", day),
         day = ifelse(ResponseID == 3192, "Monday", day),
         day = ifelse(ResponseID == 3243, "Sunday", day),
         day = ifelse(ResponseID == 3385, "Wednesday", day),
         day = ifelse(ResponseID == 3399, "Wednesday", day))

daily <- daily %>% 
  mutate(day_of_study = ifelse(ResponseID == 894, 8, day_of_study))

#run again after clean:
daily <- daily %>%
  arrange(dyadID, partID, day, RecordedDate) %>%
  mutate(ResponseID = seq_along(RecordedDate)) %>%
  group_by(partID, day) %>%
  mutate(RecordedDate_lag = lag(RecordedDate), #so we can test if record for second tuesday are plausibly next week
         dist = difftime(RecordedDate, RecordedDate_lag, units = "days"), #recoding as day between
         first_sec = seq_along(RecordedDate), #first tuesday or second tuesday?
         prob = ifelse(first_sec >= 2 & dist < 4, 1, 0)) %>% #second+ tuesday is problematic if it's NOT plausibly next week
  group_by(dyadID, partID) %>%
  arrange(dyadID, partID, RecordedDate) %>%
  mutate(rec_num = seq_along(RecordedDate),
         weekish = ifelse(rec_num > 7, 2, 1), 
         day_of_study = ifelse(weekish == 2 | (weekish==1 & first_sec>1), 
                        (case_when(day == "Monday" ~ 8,
                        day == "Tuesday" ~ 9,
                        day == "Wednesday" ~ 10,
                        day == "Thursday" ~ 11,
                        day == "Friday" ~ 12,
                        day == "Saturday" ~ 13,
                        day == "Sunday" ~ 14)), 
                      case_when(day == "Monday" ~ 1,
                        day == "Tuesday" ~ 2,
                        day == "Wednesday" ~ 3,
                        day == "Thursday" ~ 4,
                        day == "Friday" ~ 5,
                        day == "Saturday" ~ 6,
                        day == "Sunday" ~ 7)),
         week = ifelse(day_of_study > 7, 2, 1))

#selecting just what we want from daily
daily <- daily %>%
  select(partID, dyadID, RecordedDate, day, day_of_study, gender, beds:calls, 
         qmi4)

#making if they did the chore or not numeric
daily <- daily %>%
  select(-cars, -events) %>%
  mutate(beds = if_else(beds == "Yes", 1, 0),
         vacuum = if_else(vaccum == "Yes", 1, 0),
         food = if_else(food == "Yes", 1, 0),
         dishes = if_else(dishes == "Yes", 1, 0),
         garbage = if_else(garbage == "Yes", 1, 0),
         yardwork = if_else(yardwork == "Yes", 1, 0),
         pets = if_else(pets == "Yes", 1, 0),
         laundry = if_else(laundry == "Yes", 1, 0),
         errands = if_else(errands == "Yes", 1, 0),
         finances = if_else(finances == "Yes", 1, 0),
         calls = if_else(calls == "Yes", 1, 0)) %>%
  select(-vaccum) %>%
  distinct()
```

```{r}
#PREPARING FOR MERGE  
#rename the pre so that we can merge them and only include het
pre <- pre %>% 
  rename(partID = ResponseId) %>% 
  filter(sexualor == 'Heterosexual')

pre$gender <- replace(pre$gender, pre$gender == "Woman,Cis gendered", "Woman")
pre$gender <- replace(pre$gender, pre$gender == "Man,Cis gendered", "Man")

#merge the two data sets to prepare for pairwise
total <- merge(daily, pre, by = 'partID')

# Making qmi numeric
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Mostly true about me', 1)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Somewhat true about me', 2)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'A little true about me', 3)
total$qmi4 <- replace(total$qmi4, total$qmi4 == 'Not true about me', 4)
total <- total %>%
  mutate(qmi4 = as.numeric(qmi4))

#getting rid of any NAs and making them 0
total$beds[is.na(total$beds)] = 0
total$food[is.na(total$food)] = 0
total$dishes[is.na(total$dishes)] = 0
total$garbage[is.na(total$garbage)] = 0
total$yardwork[is.na(total$yardwork)] = 0
total$pets[is.na(total$pets)] = 0
total$laundry[is.na(total$laundry)] = 0
total$errands[is.na(total$errands)] = 0
total$finances[is.na(total$finances)] = 0
total$calls[is.na(total$calls)] = 0
total$vacuum[is.na(total$vacuum)] = 0
```


```{r}
#GETTING SUMS
# Summing individual daily chores
total <- total %>%
  rowwise() %>%
  mutate(ind_chores = sum(beds, food, dishes, garbage, yardwork, pets, laundry, errands, finances, calls, vacuum))

# Creating a new dataset with the sum of couple chores
couple_chores <- total %>%
  group_by(dyadID.x, day, day_of_study) %>%
  summarize(cup_chores = sum(ind_chores))

# Joining the individual and couple chore calculations 
total_chores <- merge(couple_chores, total, by = c('dyadID.x', 'day', 'day_of_study'))

# Calculating the percentage of the total chores each individual did
percent <- total_chores %>%
  group_by(dyadID.x, day, day_of_study, gender.x) %>% 
  summarize(daily_per = ifelse(cup_chores != 0, ind_chores / cup_chores, 0)) 

# Joining the individual, couple, and chore percentage calculations
final_before_pairs <- total_chores %>% 
  full_join(percent, by = c("dyadID.x", "gender.x", "day", "day_of_study"))
```

```{r}
#MAKING EVERYTHING DYADIC
# Creating a obsid
final <- final_before_pairs %>%
  mutate(obsid = day_of_study+14*(dyadID.x-1))

#finding whcih ones are greater than 2
filtered_chores <- final %>% 
  group_by(obsid) %>%
  count()

#Problems!!! we need there to only be obsid 2, anything less is fine, but anything
#above is an issue!!!
nomoreProblemshopefully <- filtered_chores %>% 
  filter(n <= 2)

#merging the set that has no problems left with the origional
fixed <- merge(nomoreProblemshopefully, final, by = 'obsid')

#putting everything in the correct order
fixed <- fixed %>% 
  select(dyadID.x, obsid, gender.x, day, day_of_study, qmi4, daily_per, bs, hs, everything())

#creating a set with just the premeasures info 
forlater <- fixed %>% 
  select(dyadID.x, obsid, day, gender.x, Q138:indinc) %>% 
  rename(dyadID = dyadID.x, 
         gender = gender.x)

# Adding gender labels and rearranging the data
pairwise <- fixed %>% 
  mutate(gender2 = gender.x, gender.x = ifelse(gender.x == 'Woman', 'A', 'P')) %>%
  select(dyadID.x, obsid, gender.x, day, day_of_study, qmi4, daily_per, bs, hs, gender2, Q138:indinc) %>% 
  rename(dyadID = dyadID.x)

# Pivoting longer
pairwise2 <- pairwise %>% 
  gather(variable, value, qmi4:Q138:indinc)

# Combining the gender and variable labels
pairwise2 <- pairwise2 %>%
  unite(var_gender, variable, gender.x) 

pairwise2 <- pairwise2 %>% 
  filter(obsid != 411584461, obsid != 411584462, obsid != 411584463, 
         obsid != 411584464, obsid != 411584465, obsid != 411584466,
         obsid != 411584467, obsid != 411584474, obsid != 411584468,
         obsid != 411584469, obsid != 411584470, obsid != 411584471,
         obsid != 411584472, obsid != 411584473)

#spread baby
pairwise2 <- pairwise2 %>% 
  pivot_wider(names_from = var_gender, values_from = value)

#filling in the categories where we know what they should be 
pairwise2$daily_per_A[is.na(pairwise2$daily_per_A)] = 0
pairwise2$daily_per_P[is.na(pairwise2$daily_per_P)] = 0
pairwise2$gender2_A[is.na(pairwise2$gender2_A)] = "Woman"
pairwise2$gender2_P[is.na(pairwise2$gender2_P)] = "Man"

# Adding gender labels and rearranging the data
pairwise3 <- fixed %>% 
  mutate(gender2 = gender.x, gender.x = ifelse(gender.x == 'Woman', 'P', 'A')) %>%
  select(dyadID.x, obsid, gender.x, day, day_of_study, qmi4, daily_per, bs, hs, gender2, Q138:indinc) %>% 
  rename(dyadID = dyadID.x)

# Pivoting longer
pairwise3 <- pairwise3 %>% 
  gather(variable, value, qmi4:indinc)

# Combining the gender and variable labels
pairwise3 <- pairwise3 %>%
  unite(var_gender, variable, gender.x)

pairwise3 <- pairwise3 %>% 
  filter(obsid != 411584461, obsid != 411584462, obsid != 411584463, 
         obsid != 411584464, obsid != 411584465, obsid != 411584466,
         obsid != 411584467, obsid != 411584474, obsid != 411584468,
         obsid != 411584469, obsid != 411584470, obsid != 411584471,
         obsid != 411584472, obsid != 411584473)

#spread baby
pairwise3 <- pairwise3 %>%
  spread(var_gender, value)

#filling in the categories where we know what they should be 
pairwise3$daily_per_A[is.na(pairwise3$daily_per_A)] = 0
pairwise3$daily_per_P[is.na(pairwise3$daily_per_P)] = 0
pairwise3$gender2_A[is.na(pairwise3$gender2_A)] = "Man"
pairwise3$gender2_P[is.na(pairwise3$gender2_P)] = "Woman"
```

```{r}
#MAKING IT PAIRWISE
#joining the datasets together
dyad_pair <- bind_rows(pairwise2, pairwise3) %>%
  arrange(obsid)
```

# Initial Model With Only Gender
```{r}
#making it so the day is subtracted by 1
dyad_pair2 <- dyad_pair %>% 
  mutate(time = day_of_study -1,
         qmi4_A = as.numeric(qmi4_A),
         time = as.numeric(time),
         daily_per_A = as.numeric(daily_per_A),
         daily_per_P = as.numeric(daily_per_P),
         hs_A = as.numeric(hs_A),
         bs_A = as.numeric(bs_A),
         hs_P = as.numeric(hs_P),
         bs_P = as.numeric(bs_P)) %>%
  filter(gender2_A == 'Woman' | gender2_A == 'Man')

#basic dyadic growth curve model (no division of labor or sexism model)
dyadicmodelbaby  <- lme(qmi4_A ~ gender2_A + gender2_A:time  - 1, #making use of two intercept model
                      #gender that is a character string and day of study is time 
                      #dont want grand intercept for everyone so use :
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time  - 1|dyadID, 
                      #using again same character string
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      #dyadic thing allows for the covariance within a particular day 
                      weights = varIdent(form = ~1|gender2_A), #get two seperate residual variances
                      na.action = na.omit)

#could use small summary or summary fully 
summary(dyadicmodelbaby)
#the outpit  is bat shit 
#where the man and women are to begin for the intercepts
#predicted overall grand slope for men and women, women are actually stable!
#mess of random effects, and all the standard deviations 
#correlations (just interpret it as a correlation matrix)
#we have done correlation matrixes
```

# Gender and Percent of Labor for Actor
```{r}
dailyandgender_A  <- lme(qmi4_A ~ gender2_A + gender2_A:time + gender2_A:daily_per_A - 1, #making use of two intercept model
                      #gender that is a character string and day of study is time 
                      #dont want grand intercept for everyone so use :
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      #using again same character string
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      #dyadic thing allows for the covariance within a particular day 
                      weights = varIdent(form = ~1|gender2_A), #get two seperate residual variances
                      na.action = na.omit)

summary(dailyandgender_A)
```
# Gender and Percent of Labor for Partner
```{r}
dailyandgender_P  <- lme(qmi4_A ~ gender2_A + gender2_A:time  + gender2_A:daily_per_P- 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(dailyandgender_P)
```

# Including the daily percent for both the partner and actor 
```{r}
#if theres no stat significant then we are going we dont combine with gender for actor
dailyandgender_Parttwo  <- lme(qmi4_A ~ gender2_A + gender2_A:time  + gender2_A:daily_per_P + gender2_A:daily_per_A - 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(dailyandgender_Parttwo)
```
# Testing if there is a difference between men and women in daily per for actor
```{r}
checkinbaby  <- lme(qmi4_A ~ gender2_A:daily_per_A - 1,
                      data = dyad_pair2, 
                      random = ~ gender2_A   - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),  
                      weights = varIdent(form = ~1|gender2_A),
                      na.action = na.omit)

summary(checkinbaby)
```
# Hostile Sexism
```{r}
justhostile <- lme(qmi4_A ~ gender2_A + gender2_A:time  + gender2_A:hs_A - 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(justhostile)
```

# Just Benevolent Sexism
```{r}
justbenevolent <- lme(qmi4_A ~ gender2_A + gender2_A:time  + gender2_A:bs_A - 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(justbenevolent)
```

# Daily per for just the actor (just for shits and giggles)
```{r}
yeall  <- lme(qmi4_A ~ gender2_A + gender2_A:time  + gender2_A:daily_per_P + gender2_A:daily_per_A  + gender2_A:hs_A + gender2_A:bs_A - 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(yeall)
```

# Adding hostile and benevolent sexism
```{r}
addingsexism  <- lme(qmi4_A ~ gender2_A + gender2_A:time + gender2_A:daily_per_P 
                     + gender2_A:daily_per_A +gender2_A:bs_A + gender2_A:hs_A - 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(addingsexism)
```

```{r}
hewo <- lme(qmi4_A ~ gender2_A + gender2_A:bs_A  + gender2_A:hs_A- 1, 
                      data = dyad_pair2, 
                      random = ~ gender2_A - 1|dyadID, 
                      correlation = corCompSymm(form = ~1|dyadID/obsid), 
                      weights = varIdent(form = ~1|gender2_A), 
                      na.action = na.omit)

summary(hewo)
```

# Playing Around
```{r}
EVERYTHING <- lme(qmi4_A ~ gender2_A + gender2_A:time + gender2_A:daily_per_A +gender2_A:bs_A + gender2_A:bs_P + gender2_A:hs_A + gender2_A:hs_P - 1, 
                  data = dyad_pair2, 
                  random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                  correlation = corCompSymm(form = ~1|dyadID/obsid), 
                  weights = varIdent(form = ~1|gender2_A), 
                  na.action = na.omit)

summary(EVERYTHING)

more_than_everything <- lme(qmi4_A ~ gender2_A + gender2_A:time + gender2_A:daily_per_A +gender2_A:bs_A + gender2_A:bs_P + gender2_A:hs_A + gender2_A:hs_P - 1, 
                  data = dyad_pair2, 
                  random = ~ gender2_A + gender2_A:time - 1|dyadID, 
                  correlation = corCompSymm(form = ~1|dyadID/obsid), 
                  weights = varIdent(form = ~1|gender2_A), 
                  na.action = na.omit)
```

#gls baby not including qmi
```{r}
helooooo <- gls(bs_A ~ gender2_A - 1 ,
                data = dyad_pair2,
                na.action = na.omit)

summary(helooooo)

```

# Pretending it isn't Dyadic for No Reason
```{r}
mod <- lm(bs_A ~ gender2_A, dyad_pair2)
anova(mod)

mod2<- lm(hs_A ~ gender2_A, dyad_pair2)
anova(mod2)

mod3 <- lm(qmi4_A ~ gender2_A*bs_A*hs_A*daily_per_A, dyad_pair2)
anova(mod3)
```

